Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added template code for age retro bar chart by sample

>>>>

###Retro

```{r GLAD/EDGI, NBR and RAMP age}

dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette4) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Age distribution of the retro cohorts",
       subtitle = paste("N =", dim(dat.retro)[1]),
       x = "Age (years)",
       y = "") +
  theme(legend.position = "bottom")
